\startchapter{Discussion, Future Work and Conclusion}
\label{chapter:discussion}

\section{Introduction}
We began this thesis with an analysis of Copilot code suggestions on Pythonic idioms, and Javascript best practices to understand the current boundaries of AI-supported code completion tools like Copilot using a software abstraction taxonomy. 
In this chapter, we first begin by extending this discussion by comparing Copilot performance on Pythonic idioms and Javascript best practices. In section~\ref{performance}, we discuss the differences in the performance and ranking of Copilot code suggestions on Pythoic idoms and JavaScript best practices. We also discuss how Copilot was able to suggest idiomatic code for some coding scenarios.

Furthermore, Having established the software abstraction hierarchy to help assess the capabilities of \cct{}, 
in section~\ref{recite}, we discuss what it means to recite code from training data of \cct{} like Copilot.
Additionally, we discuss how code recitation is an ideal behavior for \cct{} like Copilot to suggest idiomatic code but not for code smells.

In this second part of this thesis, we discussed our taxonomy of software abstractions and the challenges involved in creating \cct{} that are capable of satisfying the design level of our taxonomy. In section~\ref{implications}, we report on some implications for researchers and practitioners.
Finally, in section~\ref{limitations}, we report on the threats to the validity of the research presented in this thesis.

% We conclude this chapter by discussing how this study could be extended further, some implications for researchers and practitioners, and some future works that our study enables~(section~\ref{future}).


\input{chapters/5/ranking}
\input{chapters/5/recite}
\input{chapters/5/implications}
\input{chapters/5/limitations}
\input{chapters/5/explaninability}
\input{chapters/5/control}
\input{chapters/5/future}
\input{chapters/5/chapter_conclusion}