\section{Limitations}
\label{limitations}
Copilot and its underlying OpenAI Codex LLM are not open source. 
%Accessing them is restricted to API calls. General users cannot directly examine the model. 
We base our conclusions on API results, which makes versioning and clarity challenging. We use the current stable Copilot extension release (version: 1.30.6165) in Visual Studio Code. %The manual effort needed to query Copilot restricts the ability to use large datasets.

Copilot is sensitive to user inputs. This hurts replicability as a different formulation of the problem might produce a different set of suggestions. 
Thus a reasonable concern is that our (human) input is unfair to Copilot, and with some different inputs, the tool might generate the correct idiom. 
For replicability, we archived all examples in our replication package at \repl{}.
%\neil{can we try this? }\rohith{idioms are mostly one lined, and longer inputs/suggestions could be described as bad practices/design smells}

Our intention is admittedly to show where Copilot is not able to consistently generate the preferred answer. We biased our evaluation to highlight this by choosing input that simulates what a less experienced programmer might enter. 
But we argue this is reasonable: for one, these are precisely the developers likely to use Copilot suggestions, and unlikely to know the idiomatic usage.
More importantly, a lack of suggestion stability seems to come with its own set of challenges, equally important to understand.% (to use an analogy, we would expect all self-driving vehicles to make the similar choices when confronted with similar circumstances). 
%this gets to the top levels of Koopmann's pyramid.
% Access to Copilot is currently restricted. 
% Working with GitHub's API - not open
%
%OpenAI and open source

\section{Ethical Considerations}
\label{ethics}
Codex imports packages at different rates~\cite{copilot}, which could advantage some authors over others. As Copilot is both a \emph{black-box} and \emph{closed-source}, One can only speculate on the reasoning behind each suggestion.  For example, what sort algorithm to use. Not just a technical question but much more challenging ethically on why a particular algorithm is suggested than a flash fill kind such as a coding contest question.